---
title: "SVAP Assignment"
author: "Shashank Shekhar"
date: "10/6/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Background

I have picked Agriculture Domain. The dataset has been acuired from [here] [https://data.gov.in/catalog/district-wise-and-month-wise-queries-farmers-kisan-call-centre-kcc-during-2017] in **csv** format. The dataset is about **KCC (Kishan Call Centre)**, where Kishan (Farmer) calls to enquire/resolve issue/get information about different queries. I have picked the data fro DELHI KCC and for the month of September 2017

> Sector  : Agriculture

> Group   : Kisan Call Centre (KCC)

> Catalogs: District wise and month wise queries of farmers in Kisan Call Centre (KCC) during **September 2017** for **DELHI, INDIA**



### Frame

  - What are the top 5 **QueryType** asked in each **Category**.
  - Based on **Sept** month Data, can we predit the top KCC's queryType for October.
  
```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
library(gridExtra)
```
### Acquire
  you can get the dataset from [here] (https://data.gov.in/catalog/district-wise-and-month-wise-queries-farmers-kisan-call-centre-kcc-during-2017)
  I have taken only for **Delhi** region and for the month of **Sept'17**.
  
```{r}
getwd()
data <- read.csv("KCC.csv", header = TRUE)
str(data)
dim(data)
```

### Refine/Transform
```{r}
colnames(data) <- c('season', 'sector', 'category', 'crop', 'queryType', 'queryText', 'kccAnswer', 'state', 'district', 'block', 'createdOn')
data$season <- as.character(data$season)
data$sector <- as.character(data$sector)
data$category <- as.character(data$category)
data$crop <- as.character(data$crop)
data$queryType <- as.character(data$queryType)
data$queryText <- as.character(data$queryText)
data$kccAnswer <- as.character(data$kccAnswer)
data$state <- as.character(data$state)
data$district <- as.character(data$district)
data$block <- as.character(data$block)
data$queryType <- gsub('\t','',data$queryType)
data <- data[, 1:10] # removed createdOn column as the value in the column doesn't make sense. Also, my time frame is only for Sept'17
str(data)
dim(data)
```

### Explore

**I want to know which are top most query types which KCC gets usually.**

- This Graph shows that the **Kisan Call Centre** gets most of the calls enquiring about the `Weather`
```{r}
queryType2 <- as.data.frame.table(cbind(table(data$queryType)))

colnames(queryType2) <- c("queryType", "type", "freq")

plot1 <- queryType2 %>%
  arrange(desc(freq)) %>%
  head(12) %>% 
  ggplot(aes(reorder(queryType,freq), freq, fill=queryType)) + geom_col() + 
  coord_flip() + 
  xlab("KCC Query Type") + 
  ylab("Frequency")

plot1
```


**There are 3 districts mentioned under Delhi, Figure out which distric gets most calls**

- The Graph shows that the **EAST DELHI** has got the most calls

```{r}
queryType3 <- as.data.frame.table(cbind(table(data$district)))

colnames(queryType3) <- c("district", "type", "freq")

plot2 <- queryType3 %>%
  ggplot(aes(reorder(district,freq), freq, fill=district)) + geom_col() +
  xlab("District") + 
  ylab("Query Frequency")

plot2
```

** Which Sector gets most queries?**

- AGRICULTURE Sector leads, followed by ANIMAL HUSBANDRY & HORTICULTURE. FISHERIES is the least


```{r}
queryType4 <- as.data.frame.table(cbind(table(data$sector)))

colnames(queryType4) <- c("sector", "type", "freq")

plot3 <- queryType4 %>%
  ggplot(aes(reorder(sector,freq), freq, fill=sector)) + geom_col() +
  xlab("Sector") + 
  ylab("Query Frequency")

plot3

```

**Top 5 Query Type in each Sector**

```{r}
df<- read.csv("KCC.csv", header = TRUE)

df$QueryTypeFreq<- as.numeric(df$QueryType)

#"AGRICULTURE", "HORTICULTURE", "ANIMAL HUSBANDRY", "FISHERIES"

dfA <- df %>% 
  filter(., Sector == c("AGRICULTURE")) %>%
  arrange(desc(QueryTypeFreq)) %>%
  head(5) %>% 
  ggplot(aes(QueryType, QueryTypeFreq, color = Sector)) + geom_area(color='blue') + 
  facet_grid(Sector~.)

dfB <- df %>% 
  filter(., Sector == c("HORTICULTURE")) %>%
  arrange(desc(QueryTypeFreq)) %>%
  head(5) %>% 
  ggplot(aes(QueryType, QueryTypeFreq, color = Sector)) + geom_area(color='blue') + 
  facet_grid(Sector~.)

dfC <- df %>% 
  filter(., Sector == c("ANIMAL HUSBANDRY")) %>%
  arrange(desc(QueryTypeFreq)) %>%
  head(5) %>% 
  ggplot(aes(QueryType, QueryTypeFreq, color = Sector)) + geom_area(color='blue') + 
  facet_grid(Sector~.)

dfD <- df %>% 
  filter(., Sector == c("FISHERIES")) %>%
  arrange(desc(QueryTypeFreq)) %>%
  head(5) %>% 
  ggplot(aes(QueryType, QueryTypeFreq, color = Sector)) + geom_area(color='blue') + 
  facet_grid(Sector~.)

grid.arrange(dfA, dfB, dfC, dfD)

df %>% 
  filter(Sector == c("AGRICULTURE", "HORTICULTURE", "ANIMAL HUSBANDRY", "FISHERIES")) %>%
  ggplot(aes(reorder(QueryType, QueryTypeFreq), QueryTypeFreq , color = Sector)) + geom_area() +
  facet_grid(Sector~.) +
  coord_flip() +
  theme(axis.text = element_text(size = 3))


```




### Model

Well I am trying to predict which Secotr or Query Type would get most query in October 2017 based on Sept 2017 dataset.

```{r}
df$date <- as.Date('2017-09-01')
df2 <- df %>% 
  select(date, QueryTypeFreq)

colnames(df2) <- c('ds','y')
library(prophet)

#m<- prophet(df2)
#future <- make_future_dataframe(m, periods = 10, freq = "d")
#forecast <- predict(m, future)
#plot(m, forecast)
#tail(future)


```



### Communicate

Based on the graphs derived from the dataset, I can think of following insights

- KCC gets call for these Sectors: "AGRICULTURE", "HORTICULTURE", "ANIMAL HUSBANDRY", "FISHERIES"
- Wheater is the mosted asked query
- East Delhi gets more number of query
- Most of the query is asked for AGRICULTURE sector
- least number of query is noted from FISHERIES sector
- Central Delhi has least query