---
title: "Movie Ratings"
author: "Shashank Shekhar"
date: "10/07/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
library(gridExtra)
```

## FRAME

### Graph#1 : CEO : A diagram showing how the correlation between audience and critic ratings have evolved throughout the years by genre.
### Graph#2 : Graph between Critic and Audience. 
### Graph#3 : Which are the top 5 budget movie from Action genre?
### Graph#4 : Yearly report on max budget in each genre category
### Graph#5 : How many movies released every year in each genre category?
### Graph#6 : Which are the top 5 movies from each genre who gets high critics and auditions rating?


## ACQUIRE

```{r}
# Reading Data From **CSV** file
getwd()
mydata <- read.csv("Movie-Ratings.csv", header = TRUE)
colnames(mydata) <- c('film','genre','criticRating','audienceRating','budget','year')
str(mydata)

```

## REFINE
```{r}
# Data Conversion
mydata$film <- as.character(mydata$film)
mydata$genre <- as.character(mydata$genre)
mydata$criticRating <- mydata$criticRating/100
mydata$audienceRating <- mydata$audienceRating/100;
str(mydata)
dim(mydata)
head(mydata)
tail(mydata)

# Data Check

## Checking FILM column if there is any NA / NULL / NAN
unique(is.na(mydata$film))
unique(is.null(mydata$film))
unique(is.nan(mydata$film))

## Checking GENRE column if there is any NA / NULL / NAN
unique(is.na(mydata$genre))
unique(is.null(mydata$genre))
unique(is.nan(mydata$genre))

## Checking CRICTIC RATING column if there is any NA / NULL / NAN. Also the CRICTIC RATING cannot be negative or more than 100%
unique(is.na(mydata$criticRating))
unique(is.null(mydata$criticRating))
unique(is.nan(mydata$criticRating))

mydata %>%
  filter(criticRating < 1) %>%
  filter(criticRating < 0)

## Checking AUDIENCE RATING column if there is any NA / NULL / NAN. Also the AUDIENCE RATING cannot be negative or more than 100%
unique(is.na(mydata$audienceRating))
unique(is.null(mydata$audienceRating))
unique(is.nan(mydata$audienceRating))

mydata %>%
  filter(audienceRating > 1) %>%
  filter(audienceRating < 0)

## Checking BUDGET column if there is any NA / NULL / NAN. Also the BUDGET cannot be negative
unique(is.na(mydata$budget))
unique(is.null(mydata$budget))
unique(is.nan(mydata$budget))

mydata %>%
  filter(budget < 0)

## Checking YEAR column if there is any NA / NULL / NAN. Also year length is equal to 4
unique(is.na(mydata$year))
unique(is.null(mydata$year))
unique(is.nan(mydata$year))

mydata %>%
  filter(nchar(year) != 4) 


df <- mydata

```

## GRAPHS
```{r}
## Graph#1 : CEO : A diagram showing how the correlation between audience and critic ratings have evolved throughout the years by genre.
 df %>%
  group_by(year, genre) %>% 
  summarise(corel = cor(audienceRating, criticRating))  %>%
  ggplot(aes(year, corel, color=genre)) + 
  geom_line() + 
  xlab("Year") +
  ylab("Correlation between Audience and Critic Rating")
```
```{r}
## Graph#2 : Graph between Critic and Audience 
df %>%
  group_by(year) %>% 
  ggplot(aes(criticRating, audienceRating, color=year)) +
  geom_line() +
  xlab("Critic Rating") +
  ylab("Audience Rating")
```
```{r}
#Graph#3 : Which are the top 5 budget movie from Action genre?
df %>%
  filter(genre == c("Action")) %>% 
  arrange(desc(budget)) %>% 
  head(5) %>% 
  ggplot(aes(reorder(film, budget), budget, fill=budget)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  xlab("Film") + 
  ylab("Budget")  +
  scale_colour_discrete(guide = 'none') +
  scale_x_discrete(expand=c(0, 1)) +
  ggtitle("Genre : Action", subtitle = "Top 5 budget movie of all the time")


```

```{r}
#Graph#4 : Yearly report on max budget in each genre category
library(plotly)
a <- df %>%
  group_by(genre, year) %>%
  summarise(total = sum(budget)) %>%
  ggplot(aes(year, total, fill=genre)) + 
  geom_bar(stat = "identity") +
  xlab("Year") +
  ylab("Budget") +
  ggtitle("Yearly Report - Budget spent on Genre", subtitle = NULL)

ggplotly(a)

```


```{r}
#Graph#5 : How many movies released every year in each genre category?
b <- df %>%
  group_by(genre, year) %>%
  summarise(total = sum(as.integer(as.factor(genre)))) %>%
  ggplot(aes(year, total, fill=genre )) +
  geom_bar(stat = "identity")  +
  xlab("Year")  +
  ylab("# Of Films")  +
  ggtitle("# Of Films Each Year & By Genre", subtitle = "") 
  
ggplotly(b)
```

```{r}
#Graph 6: Which are the top 5 movies from each genre who gets high critics and auditions rating?

a1 <- df %>%
  filter(genre == c("Comedy")) %>% 
  arrange(desc(budget)) %>% 
  head(5) %>% 
  ggplot(aes(reorder(film, budget), budget, fill=budget)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  xlab("Film") + 
  ylab("Budget")  +
  scale_colour_discrete(guide = 'none') +
  scale_x_discrete(expand=c(0, 1)) +
  ggtitle("Genre : Comedy", subtitle = "Top 5 budget movie of all the time")

a2 <- df %>%
  filter(genre == c("Adventure")) %>% 
  arrange(desc(budget)) %>% 
  head(5) %>% 
  ggplot(aes(reorder(film, budget), budget, fill=budget)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  xlab("Film") + 
  ylab("Budget")  +
  scale_colour_discrete(guide = 'none') +
  scale_x_discrete(expand=c(0, 1)) +
  ggtitle("Genre : Adventure", subtitle = "Top 5 budget movie of all the time")

a3 <- df %>%
  filter(genre == c("Action")) %>% 
  arrange(desc(budget)) %>% 
  head(5) %>% 
  ggplot(aes(reorder(film, budget), budget, fill=budget)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  xlab("Film") + 
  ylab("Budget")  +
  scale_colour_discrete(guide = 'none') +
  scale_x_discrete(expand=c(0, 1)) +
  ggtitle("Genre : Action", subtitle = "Top 5 budget movie of all the time")

a4 <- df %>%
  filter(genre == c("Horror")) %>% 
  arrange(desc(budget)) %>% 
  head(5) %>% 
  ggplot(aes(reorder(film, budget), budget, fill=budget)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  xlab("Film") + 
  ylab("Budget")  +
  scale_colour_discrete(guide = 'none') +
  scale_x_discrete(expand=c(0, 1)) +
  ggtitle("Genre : Horror", subtitle = "Top 5 budget movie of all the time")

a5 <- df %>%
  filter(genre == c("Drama")) %>% 
  arrange(desc(budget)) %>% 
  head(5) %>% 
  ggplot(aes(reorder(film, budget), budget, fill=budget)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  xlab("Film") + 
  ylab("Budget")  +
  scale_colour_discrete(guide = 'none') +
  scale_x_discrete(expand=c(0, 1)) +
  ggtitle("Genre : Drama", subtitle = "Top 5 budget movie of all the time")

a6 <- df %>%
  filter(genre == c("Romance")) %>% 
  arrange(desc(budget)) %>% 
  head(5) %>% 
  ggplot(aes(reorder(film, budget), budget, fill=budget)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  xlab("Film") + 
  ylab("Budget")  +
  scale_colour_discrete(guide = 'none') +
  scale_x_discrete(expand=c(0, 1)) +
  ggtitle("Genre : Romance", subtitle = "Top 5 budget movie of all the time")

a7 <- df %>%
  filter(genre == c("Thriller")) %>% 
  arrange(desc(budget)) %>% 
  head(5) %>% 
  ggplot(aes(reorder(film, budget), budget, fill=budget)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  xlab("Film") + 
  ylab("Budget")  +
  scale_colour_discrete(guide = 'none') +
  scale_x_discrete(expand=c(0, 1)) +
  ggtitle("Genre : Thriller", subtitle = "Top 5 budget movie of all the time")

grid.arrange(a1, a2)
grid.arrange(a3, a4)
grid.arrange(a5, a6)
grid.arrange(a7, nrow=2)


```
